Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections

### 2025-06-03 index.qmd
Updated formatting of html

# set some session options for `tinytable`
options(tinytable_tt_digits = 3)
# options(tinytable_theme_placement_latex_float = "H")
options(tinytable_html_mathjax = TRUE) # set option to render math in html

@@

trust_txt <- data |> select(q19, q20, q21, q22, q24) |>
  labelled::set_variable_labels(
    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
  ) |> 
  labelled::generate_dictionary() |> 
  dplyr::as_tibble() |> 
  dplyr::select(Trust=label)

distrust_txt <- data |> select(q28_1:q28_5) |>
  labelled::generate_dictionary() |> 
  dplyr::as_tibble() |> 
  dplyr::select(Distrust=label)

conf_items_text <- trust_txt |> 
  mutate(Distrust = pull(distrust_txt))

tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
  tinytable::style_tt(fontsize = 0.80)

@@

# Output using `tinytable` R Package
colnames(tab_ttest) <- c(
  "Place",
  "$\\bar{x}_{diff}$",
  "$\\bar{x}_{treat}$",
  "$\\bar{x}_{control}$",
  "$n_{treat}$",
  "$n_{control}$",
  "t",
  "p",
  "df",
  "CI")

tinytable::tt(tab_ttest) |>
  tinytable::format_tt(
    j = 2:6, # specify columns  
    math = T # apply mathmode to specified columns
  ) |> 
  tinytable::style_tt(fontsize = 0.75) # fontsize in em units (0.75*default fontsize)

@@

tinytable::tt(
  tab_q25_pdiff,
  notes = "Results derived from proportional odds logistic regression model. Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |> 
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |>  
  tinytable::style_tt(i = "notes", fontsize = 0.75)

@@

tinytable::tt(
  tab_q26_pdiff,
  notes = "Results derived from proportional odds logistic regression model. Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>  
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |>  
  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes

@@

```{r}
#| label: tbl-4
#| tbl-cap: "Survey Items and Response Options"
#| tbl-colwidths: [70, 30]

@@

tbl.desc |> 
  gtsummary::as_tibble() |> 
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  dplyr::select(-"**N**") |> 
  tinytable::tt(theme = "spacing") |> 
  tinytable::format_tt(markdown = T) |> 
  tinytable::format_tt(replace = " ") |> 
  tinytable::style_tt(fontsize = 0.70)

@@

# using `rbind2` function, bind 2nd table at bottom of first table 
tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
  # add horizontal line just above fit stats
  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
  # adjust fontsize of text within table
  tinytable::style_tt(fontsize = 0.8) |>
  # finally, format markdown and blank out any NA fillers
  tinytable::format_tt(markdown = T, replace = " ")

@@

tbl_safety_logit |>  
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75)

@@

tinytable::tt(
  tab_safety_preds1, digits = 3,
  notes = attr(data$q25, "label")) |> 
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75)

@@

tinytable::tt(
  tab_safety_preds2, digits = 3,
  notes = attr(data$q26, "label")) |>  
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75)

>>>>

# set some session options for `tinytable`
options(tinytable_tt_digits = 3)
# set option to render tinytable math in html
options(tinytable_html_mathjax = TRUE)

# options(tinytable_quarto_disable_processing = FALSE)
# options(tinytable_theme_placement_latex_float = "H")

@@

trust_txt <- data |> 
  dplyr::select(q19, q20, q21, q22, q24) |>
  labelled::set_variable_labels(
    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
  ) |> 
  labelled::generate_dictionary() |> 
  dplyr::as_tibble() |> 
  dplyr::select(Trust=label)

distrust_txt <- data |> 
  dplyr::select(q28_1:q28_5) |>
  labelled::generate_dictionary() |> 
  dplyr::as_tibble() |> 
  dplyr::select(Distrust=label)

conf_items_text <- trust_txt |> 
  dplyr::mutate(Distrust = dplyr::pull(distrust_txt))

tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
  tinytable::style_tt(fontsize = 0.80, align = "ll")

@@

# convert from `data.frame` to `tinytable` class object
tab_ttest <- tinytable::tt(tab_ttest)

# modify column names of table
colnames(tab_ttest) <- c(
  "Place",
  "$\\bar{x}_{diff}$",
  "$\\bar{x}_{treat}$",
  "$\\bar{x}_{control}$",
  "$n_{treat}$",
  "$n_{control}$",
  "t",
  "p",
  "df",
  "CI")

# Output using `tinytable` R Package
tab_ttest |> 
  tinytable::format_tt(
    j = 2:6, # specify columns
    math = T # apply mathmode to specified columns
  ) |> 
  tinytable::style_tt(
    fontsize = 0.75, # fontsize in em units (0.75*default fontsize)
    align = "lccccccccc"
    )

@@

tinytable::tt(
  tab_q25_pdiff,
  notes = "Results derived from proportional odds logistic regression model. Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |> 
  tinytable::style_tt(
    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
    align = "lcccccc"
    ) |>  
  tinytable::style_tt(i = "notes", fontsize = 0.75)

@@

tinytable::tt(
  tab_q26_pdiff,
  notes = "Results derived from proportional odds logistic regression model. Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>  
  tinytable::style_tt(
    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
    align = "lcccccc"
    ) |>  
  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes

@@

```{r}
#| label: tbl-4
#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
#| tbl-colwidths: [70, 30]

@@

tbl.desc |> 
  gtsummary::as_tibble() |> 
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  dplyr::select(-"**N**") |> 
  tinytable::tt(theme = "spacing") |> 
  tinytable::format_tt(markdown = T) |> 
  tinytable::format_tt(replace = " ") |> 
  tinytable::style_tt(fontsize = 0.70, align = "lccc")

@@

# using `rbind2` function, bind 2nd table at bottom of first table 
tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
  # add horizontal line just above fit stats
  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
  # adjust fontsize of text within table
  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
  # finally, format markdown and blank out any NA fillers
  tinytable::format_tt(markdown = T, replace = " ")

@@

tbl_safety_logit |>  
  tinytable::style_tt(
    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
    ) |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")

@@

tinytable::tt(
  tab_safety_preds1, digits = 3,
  notes = attr(data$q25, "label")) |> 
  tinytable::style_tt(
    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
    align = "llccccc") |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")

@@

tinytable::tt(
  tab_safety_preds2, digits = 3,
  notes = attr(data$q26, "label")) |>  
  tinytable::style_tt(
    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
    align = "llccccc"
    ) |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75)
